Manuscript_Tables_LongCovid

### 2023-01-10 characterisation/Manuscript_Tables_Figures.Rmd
Update Manuscript_Tables_Figures.Rmd

@@

get_rr_infection_negative_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
    scale_x_log10(breaks = c(0.5, 0.8, 1,2, 4, 6),
                  labels = c("0.5","0.8", "1","2", "4", "6"),
                  limits = c(0.5, 8)) +  
    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

get_rr_first_reinfection_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, -relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
                  limits = c(0.04, 1.2)
                  ) +  
    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

@@

## Main results
### Table 1: Baseline characteristics of individuals with COVID-19 and tested negative (earliest record)

```{r echo=FALSE}
table1 <- get_baseline_main_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1
```

### Figure 1: Incidence rates of COVID-19 and long-COVID-19

```{r, fig.dim = c(8, 8), echo = FALSE}
Incidence_rates_Covid_LongCov_SIDIAP$time <- NULL
Incidence_rates_Covid_LongCov_CPRD <- Incidence_rates_Covid_LongCov_CPRD %>%
  rename(ir_100000_pys = incidence_100000_pys,
         ir_100000_pys_95CI_lower = incidence_100000_pys_95CI_lower,
         ir_100000_pys_95CI_upper = incidence_100000_pys_95CI_upper)
IR_data <- rbind(Incidence_rates_Covid_LongCov_CPRD, Incidence_rates_Covid_LongCov_SIDIAP)
Proportion_data <- rbind(Proportion_LongCovid_90days_CPRD, Proportion_LongCovid_90days_SIDIAP)

@@

plot_IR_overall <- function(age_to_filter, data){ 
  plot <- data %>%
  filter(age_group %in% age_to_filter) %>%
  ggplot() +
#  geom_smooth(aes(x =incidence_start_date, y =  ir_100000_pys), method="auto", se=TRUE, fullrange=FALSE, level=0.95)+
geom_line(aes(x =incidence_start_date, y =  ir_100000_pys, color = database), size = 1.2)+
geom_ribbon(aes(x =incidence_start_date, y =  ir_100000_pys,
                ymin = ir_100000_pys_95CI_lower, ymax = ir_100000_pys_95CI_upper,
                group= database
                ), alpha = 0.3) +
scale_y_continuous(limits = c(0,NA)) +
scale_x_date(date_breaks = "2 month",
               date_labels = ("%b %y"),
               expand = c(0,0)) +
        scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
  theme_bw()+
  theme(legend.position="top",
        plot.margin = unit(c(0.1, 0.5, 0.1, 0.1), "cm"),
        strip.text.y = element_text(angle = 0),
    strip.background =element_rect(fill="#F5F5F5")) +
  ylab("IR per 100,000 p-y") +
    facet_wrap(~cohort, scales = "free_y", ncol = 1) +
 # facet_grid(rows = vars(cohort),
 #            scales = "fixed") +
    xlab("Date of COVID-19 infection") +
        guides(color = guide_legend(title = "Database"), 
               fill = guide_legend(title = "Database"))
   plot         
  }

@@

### Figure 2: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

@@

### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}
RR_data <- rbind(RR_first_infection_reinfections_90days_SIDIAP,
                  RR_first_infection_reinfections_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

@@

## Supplementary
### Baseline characteristics and symptoms distribution
#### 1. Table: Baseline characteristics of first infections, re-infections and all negative SARS-CoV-2 tests records

```{r}
table1_sup <- get_baseline_sup_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1_sup
```

#### 2. Table: Symptoms distribution across cohorts (unmatched) - 90 days

```{r}
get_symptoms_main_table(sidiap_data = Table1_90days_SIDIAP, 
                        cprd_data = Table1_90days_CPRD)
```

#### 3. Table: Symptoms distribution across cohorts (unmatched) - 28 days

```{r}
get_symptoms_main_table(sidiap_data = Table1_28days_SIDIAP, 
                        cprd_data = Table1_28days_CPRD)
```

#### 4. Table: Baseline characteristics - COVID-19 infection vs first negative test matched 3:1

```{r echo=FALSE}
Sup_table_matched_negative_90 <- get_matched_table_negative(
  sidiap_data = Table_Matched_Infection_Tested_Negative_earliest_90days_SIDIAP,
  cprd_data = Table_Matched_Infection_Tested_Negative_earliest_90days_CPRD)
Sup_table_matched_negative_90 
```

#### 5. Table: Baseline characteristics: first COVID-19 infection vs re-infections matched 1:3

```{r echo=FALSE}
Sup_table_matched_first_reinfection_90 <- get_matched_table_first_reinfection(
  sidiap_data = Table_Matched_First_infection_Reinfections_90days_SIDIAP,
  cprd_data = Table_Matched_First_infection_Reinfections_90days_CPRD)
Sup_table_matched_first_reinfection_90 
```
### Incidence Rates
#### 1. Table: Incidence Rates of COVID-19 & long COVID symptoms

```{r}

@@

#### 2. Figure: Incidence Rates by Sex and Age group
##### A. SIDIAP

```{r echo=FALSE}

@@

##### B. CPRD

```{r echo=FALSE}

@@

#### 2. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days

```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
table_RR_28
```

#### 3. Figure: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_28days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

@@

### Relative Risks - re-infections vs first infection
#### 1. Table: RR of long-COVID symptoms, first infection vs re-infection - 90 days

```{r}
get_RR_numbers_re_infec <- function(sidiap_data, cprd_data) {
  RR_infections <- rbind(sidiap_data, cprd_data
                      ) %>%
  mutate(relative_risk = paste0(sprintf(relative_risk, fmt = '%.2f'),
                                " [",
                                sprintf(low_ci, fmt = '%.2f'),
                                ";",
                                sprintf(up_ci, fmt = '%.2f'),
                                "]"
         )) %>%
    select (-prop_1, -prop_2, -low_ci, -up_ci, 
                        -name_1, -name_2, -total_pop_1, -total_pop_2,) %>%
    relocate(database,.before = symptom)  %>%
    arrange(desc(database),relative_risk)

@@

#### 3. Figure: RR of long-COVID symptoms, first infection vs re-infection - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}

@@

#### 2. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}

@@

#### 4. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}

>>>>

col1 <- "#3A6D82"
col2 <- "#9F5339"

@@

get_rr_infection_negative_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
    scale_x_log10(breaks = c(0.5, 0.8, 1,2, 4, 6),
                  labels = c("0.5","0.8", "1","2", "4", "6"),
                  limits = c(0.5, 8)) +  
    scale_colour_manual(values = c(col1, col2)) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

get_rr_first_reinfection_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, -relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
                  limits = c(0.04, 1.2)
                  ) +  
    scale_colour_manual(values = c(col1, col2)) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

@@

## Main results
### Table 1: Baseline characteristics of individuals with COVID-19 and tested negative (earliest record)
```{r echo=FALSE}
table1 <- get_baseline_main_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1
```

### Figure 1: Incidence rates of COVID-19 and long-COVID-19
```{r, fig.dim = c(8, 8), echo = FALSE}
Incidence_rates_Covid_LongCov_SIDIAP$time <- NULL
Incidence_rates_Covid_LongCov_CPRD <- Incidence_rates_Covid_LongCov_CPRD %>%
  rename(ir_100000_pys = incidence_100000_pys,
         ir_100000_pys_95CI_lower = incidence_100000_pys_95CI_lower,
         ir_100000_pys_95CI_upper = incidence_100000_pys_95CI_upper)
IR_data <- rbind(Incidence_rates_Covid_LongCov_CPRD, Incidence_rates_Covid_LongCov_SIDIAP)
Proportion_data <- rbind(Proportion_LongCovid_90days_CPRD, Proportion_LongCovid_90days_SIDIAP)

@@

plot_IR_overall <- function(age_to_filter, data){ 
  plot <- data %>%
  filter(age_group %in% age_to_filter) %>%
  ggplot() +
#  geom_smooth(aes(x =incidence_start_date, y =  ir_100000_pys), method="auto", se=TRUE, fullrange=FALSE, level=0.95)+
geom_line(aes(x =incidence_start_date, y =  ir_100000_pys, color = database), size = 1.2)+
geom_ribbon(aes(x =incidence_start_date, y =  ir_100000_pys,
                ymin = ir_100000_pys_95CI_lower, ymax = ir_100000_pys_95CI_upper,
                group= database
                ), alpha = 0.3) +
scale_y_continuous(limits = c(0,NA)) +
scale_x_date(date_breaks = "2 month",
               date_labels = ("%b %y"),
               expand = c(0,0)) +
        scale_colour_manual(values = c(col1, col2)) +
  theme_bw()+
  theme(legend.position="top",
        plot.margin = unit(c(0.1, 0.5, 0.1, 0.1), "cm"),
        strip.text.y = element_text(angle = 0),
    strip.background =element_rect(fill="#F5F5F5")) +
  ylab("IR per 100,000 p-y") +
    facet_wrap(~cohort, scales = "free_y", ncol = 1) +
 # facet_grid(rows = vars(cohort),
 #            scales = "fixed") +
    xlab("Date of COVID-19 infection") +
        guides(color = guide_legend(title = "Database"), 
               fill = guide_legend(title = "Database"))
   plot         
  }

@@

### Figure 2: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

@@

### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days
```{r, fig.dim = c(8, 8), echo = FALSE}
RR_data <- rbind(RR_first_infection_reinfections_90days_SIDIAP,
                  RR_first_infection_reinfections_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

@@

## Supplementary
### Baseline characteristics and symptoms distribution
#### 1. Table: Baseline characteristics of first infections, re-infections and all negative SARS-CoV-2 tests records
```{r}
table1_sup <- get_baseline_sup_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1_sup
```

#### 2. Table: Symptoms distribution across cohorts (unmatched) - 90 days
```{r}
get_symptoms_main_table(sidiap_data = Table1_90days_SIDIAP, 
                        cprd_data = Table1_90days_CPRD)
```

#### 3. Table: Symptoms distribution across cohorts (unmatched) - 28 days
```{r}
get_symptoms_main_table(sidiap_data = Table1_28days_SIDIAP, 
                        cprd_data = Table1_28days_CPRD)
```

#### 4. Table: Baseline characteristics - COVID-19 infection vs first negative test matched 3:1
```{r echo=FALSE}
Sup_table_matched_negative_90 <- get_matched_table_negative(
  sidiap_data = Table_Matched_Infection_Tested_Negative_earliest_90days_SIDIAP,
  cprd_data = Table_Matched_Infection_Tested_Negative_earliest_90days_CPRD)
Sup_table_matched_negative_90 
```

#### 5. Table: Baseline characteristics: first COVID-19 infection vs re-infections matched 1:3
```{r echo=FALSE}
Sup_table_matched_first_reinfection_90 <- get_matched_table_first_reinfection(
  sidiap_data = Table_Matched_First_infection_Reinfections_90days_SIDIAP,
  cprd_data = Table_Matched_First_infection_Reinfections_90days_CPRD)
Sup_table_matched_first_reinfection_90 
```

### Incidence Rates
#### 1. Table: Incidence Rates of COVID-19 & long COVID symptoms
```{r}

@@

#### 2. Figure: Incidence Rates by Sex and Age group
##### A. SIDIAP
```{r echo=FALSE}

@@

##### B. CPRD
```{r echo=FALSE}

@@

#### 2. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
table_RR_28
```

#### 3. Figure: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_28days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

@@

### Relative Risks - re-infections vs first infection
#### 1. Table: RR of long-COVID symptoms, first infection vs re-infection - 90 days
```{r}
get_RR_numbers_re_infec <- function(sidiap_data, cprd_data) {
  RR_infections <- rbind(sidiap_data, cprd_data
                      ) %>%
  mutate(relative_risk = paste0(sprintf(relative_risk, fmt = '%.2f'),
                                " [",
                                sprintf(low_ci, fmt = '%.2f'),
                                ";",
                                sprintf(up_ci, fmt = '%.2f'),
                                "]"
         )) %>%
    select (-prop_1, -prop_2, -low_ci, -up_ci, 
                        -name_1, -name_2, -total_pop_1, -total_pop_2,) %>%
    relocate(database,.before = symptom)  %>%
    arrange(desc(database),relative_risk)

@@

#### 3. Figure: RR of long-COVID symptoms, first infection vs re-infection - 28 days
```{r, fig.dim = c(8, 8), echo = FALSE}

@@

#### 2. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days
```{r, fig.dim = c(8, 8), echo = FALSE}

@@

#### 4. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days
```{r, fig.dim = c(8, 8), echo = FALSE}
